Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-30 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Adding new example, and delete the old one...

Intuitively, the expectation value of an observable with respect to
an IVPM should be the minimum and maximum expectation value of the
same observable with respect to its consistent states. We found this
is true when we require our IVPM to be convex, and on a commuting
sub-event space, whose definition is given as follow.

@@

For example, to compute the expectation value of $\sigma_{\mathrm{z}}=\proj{0}-\proj{1}$
with respect to $\bar{\mu}_{1}$, we have $N^{+}=N^{-}=1$, $\lambda_{1}^{+}=1$,
$\lambda_{1}^{-}=-1$, $P_{1}^{+\prime}=\proj{0}$, $P_{1}^{-\prime}=\proj{1}$,
$P_{2}^{+\prime}=P_{2}^{-\prime}=\mathbb{0}$. Let $\left[\mul_{1}\left(E\right),\mur_{1}\left(E\right)\right]=\bar{\mu}_{1}\left(E\right)$,
then $\Delta\mul_{1}\left(P_{1}^{+\prime}\right)=\mul_{1}\left(\proj{0}\right)-\mul_{1}\left(\mathbb{0}\right)=0$,
$\Delta\mul_{1}\left(P_{1}^{-\prime}\right)=\mul_{1}\left(\proj{1}\right)-\mul_{1}\left(\mathbb{0}\right)=0$,
$\Delta\mur_{1}\left(P_{1}^{+\prime}\right)=\mur_{1}\left(\proj{0}\right)-\mur_{1}\left(\mathbb{0}\right)=1$,
$\Delta\mur_{1}\left(P_{1}^{-\prime}\right)=\mur_{1}\left(\proj{1}\right)-\mur_{1}\left(\mathbb{0}\right)=1$.
Therefore, $\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}=\left[0,1\right]+\left(-1\right)\left[0,1\right]=\left[-1,1\right]$.

On the other hand, it is easy to verify that $\bar{\mu}_{1}$ is convex.
Every state is consistent with $\bar{\mu}_{1}$, in particular $\proj{0}$
and $\proj{1}$. It is easy to see\begin{subequations}
\begin{eqnarray}
\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{1}}=-1\textrm{ ,}\\
\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{0}}=1\textrm{ ,}
\end{eqnarray}
\end{subequations}which is consistent with the theorem.

In contrast to the usual identity~$\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\rho}=\expval{\mathbf{O}_{1}}_{\rho}+\expval{\mathbf{O}_{2}}_{\rho}$,
we have
\begin{equation}
\expval{\mathbb{0}}_{\bar{\mu}_{1}}=\left[0,0\right]\subsetneq\left[-2,2\right]=\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}+\expval{-\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}
\end{equation}
because the precision is easily be lost when applying arithmetic operations.
In general, when $\bar{\mu}$ is convex, we have 
\begin{equation}
\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\bar{\mu}}\subseteq\expval{\mathbf{O}_{1}}_{\bar{\mu}}+\expval{\mathbf{O}_{2}}_{\bar{\mu}}\textrm{ ,}
\end{equation}
for commuting $\mathbf{O}_{1}$ and $\mathbf{O}_{2}$.

>>>>

\begin{table*}
\caption{\label{table:quantum-interval-expectation}This table highlight the
process to compute $\expval{\mathbf{O}}_{\bar{\mu}_{1}}$. Notice
that $\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$
and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$. }

\begin{ruledtabular}
\begin{tabular}{c|ccccccccc}
$i$ & $\lambda_{i}^{+}$ & $P_{i}^{+}$ & $\bar{\mu}_{1}\left(P_{i}^{+}\right)$ & $P_{i}^{+\prime}$ & $\bar{\mu}_{1}\left(P_{i}^{+\prime}\right)$ & $\mul_{1}\left(P_{i}^{+\prime}\right)$ & $\mur_{1}\left(P_{i}^{+\prime}\right)$ & $\Delta\mul_{1}\left(P_{i}^{+\prime}\right)$ & $\Delta\mur_{1}\left(P_{i}^{+\prime}\right)$\tabularnewline
\hline 
$1$ & $1$ & $\proj{0}+\proj{2}$ & $\unknown$ & $\mathbb{1}$ & $\necess$ & $1$ & $1$ & $1$ & $0$\tabularnewline
$2$ & $2$ & $\proj{1}$ & $\unknown$ & $\proj{1}$ & $\unknown$ & $0$ & $1$ & $0$ & $1$\tabularnewline
\end{tabular}
\end{ruledtabular}

\end{table*}
Since Eq.~(\ref{eq:quantum-interval-expectation}) is more complex
than Eq.~(\ref{eq:quantum-expectation}), it is instructive to check
an example. Given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $J_{\mathrm{z}}=\proj{0}-\proj{2}$,
and $\mathbf{O}=2\mathbb{1}-J_{\mathrm{z}}^{2}=2\proj{1}+\proj{0}+\proj{2}$.
By following Table~\ref{table:quantum-interval-expectation}, we
have 
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\textrm{ .}
\end{equation}
$\left[1,2\right]$ is an intuitively result. Since two possible outcomes
are $1$ and $2$, the expectation value is between one of them even
if we no prior knowledge about the likelihood of outcomes. In contrast,
if we naively multiply eigenvalues with intervals, their sum is $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$
which is a worse estimation. Because even if we no prior knowledge,
we know one of them will happen, and estimating the lower-bound by$1\cdot0+2\cdot0=0$
is too pessimistic.

Formally, the expectation value of an observable with respect to an
IVPM should intuitively be the minimum and maximum expectation value
of the same observable with respect to its consistent states. We found
this is true when we require our IVPM to be convex, and on a commuting
sub-event space, whose definition is given as follow.

@@
